---
title: "Logit ATL results"
output: html_document
date: "2024-08-29"


---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(mice)
library(miceadds)
library(mitools)
library(sandwich)
library(survey)
library(naniar)
```

## Descriptives - w MI DATA
```{r}
desc.long <- complete(imp, "long", include = F) # long format WITHOUT OG data

cont.vars <- c("x2kage_r", "x1tchapp" , "x2tchapp", "x2prnapp", "x2pltot", "x2clsnss", "x2cnflct", "x2inbcnt","x2attnfs")

cat.vars <- c("cat.atl", "x_chsex_r", "x2povty", "kndr_par_ed", "x2locale", "x2pubpri")

age.mean <- with(imp, lm(x2kage_r~1))
summary(pool(age.mean))

atl.mean.f <- with(imp, lm(x1tchapp~1))
summary(pool(atl.mean.f))

atl.mean.s <- with(imp, lm(x2tchapp~1))
summary(pool(atl.mean.s))

parnt.atl.mean <- with(imp, lm(x2prnapp~1))
summary(pool(parnt.atl.mean))

lang.mean <- with(imp, lm(x2pltot~1))
summary(pool(lang.mean))

cls.mean <- with(imp, lm(x2clsnss~1))
summary(pool(cls.mean))

cnflct.mean <- with(imp, lm(x2cnflct~1))
summary(pool(cnflct.mean))

inhb.mean <- with(imp, lm(x2inbcnt~1))
summary(pool(inhb.mean))

attn.mean <- with(imp, lm(x2attnfs~1))
summary(pool(attn.mean))

imp.corr <- miceadds::micombine.cor(mi.res = imp, variables = cont.vars)
attr(imp.corr, "r_matrix")

rbind(mi.n.p(imp, "cat.atl"))

rbind(mi.n.p.by(imp, "cat.atl", BY = "x_chsex_r"))
rbind(mi.n.p.by(imp, "cat.atl", BY = "x2povty"))
rbind(mi.n.p.by(imp, "cat.atl", BY = "kndr_par_ed"))
#splits between groups may not be even between imputations 
```
## Prep for Sample Weights 
```{r}
#attempting to run weighted regression on imputed data sets 
#return after obtaining non-weighted results - 9/17 

wghtd.imp <- complete(imp, "all", include = T)
create_survey_designs <- function(imp_list) {
  # Extract only the imputed datasets (skip index 0)
  imp_datasets <- imp_list[-1]  # Skip the first dataset, which is the original data
  
  # Create survey design objects for each imputed dataset
  lapply(imp_datasets, function(df_list) {
    # Extract the data frame
    df <- df_list[[1]]  # Assuming the data frame is the first element of the list
    
    # Extract the cluster variable and weights
    s2_id <- df_list[["s2_id"]]
    w12t0 <- df_list[["w12t0"]]
    
    # Ensure the data frame contains the necessary columns
    stopifnot("s2_id" %in% colnames(df))
    stopifnot("w12t0" %in% colnames(df))
    
    # Create the survey design object
    svydesign(ids = ~s2_id, weights = ~w12t0, nested = TRUE, data = df)
  })
}

k.design <- create_survey_designs(wghtd.imp)



logit.model <- svyglm(cat.atl ~ x1tchapp, 
                      family="binomial", design = k.design)
k.design <- svydesign(ids=~s2_id, weights = ~w12t0, data=desc.long, nested=T)
wghtd.model <- with(imp, logit.model)
summary(pool(wghtd.model))
```


## Model choices

#Logistic Regression - separate closeness/conflict Models - Clustered SE
```{r}
#correlations 

kinder.corr <- kinder.corr %>% as.data.frame() 
kinder.corr <- tibble::rownames_to_column(kinder.corr, "Variable")

gt.corr <- kinder.corr %>% gt() %>% 
  tab_header(
    title = "Correlation Matrix for Cont. Variables"
  ) %>%
  fmt_number(
    columns = -Variable, # Apply formatting to all numeric columns except 'Variable'
    decimals = 2 # Round to 2 decimal places
  ) %>%
  data_color(
    columns = -Variable, # Apply color formatting to the correlation values
    colors = scales::col_numeric(
      palette = c("blue", "white", "red"), # Color gradient from blue to red
      domain = c(-1, 1) # Set the range from -1 to 1 for correlations
    )
  ) %>%
  tab_options(
    table.font.size = "small", # Adjust font size
    table.width = "auto"       # Make table width adaptive
  ) %>%
  tab_style(
    style = list(
      cell_borders(sides = "all", color = "gray", weight = px(1))
    ),
    locations = cells_body(columns = everything())
  ) %>%
  cols_label(
    Variable = " "
  )

gt.corr

apa.corr <- kinder.corr %>% gt() %>% 
  tab_header( title = "Correlation Matrix"
  ) %>%
  fmt_number(
    columns = -Variable, # Apply formatting to all numeric columns except 'Variable'
    decimals = 2 # Round to 2 decimal places
  ) %>%
  cols_label(
    Variable = "" # Remove the label for the 'Variable' column for APA style
  ) %>%
  tab_options(
    table.border.top.style = "none", # Remove top border
    table.border.bottom.style = "none", # Remove bottom border
    table_body.hlines.style = "none", # Remove horizontal lines between rows
    table_body.vlines.style = "none", # Remove vertical lines between columns
    table.font.size = "medium", # Use medium font size for readability
    table.align = "center" # Center align the table
  ) %>%
  tab_style(
    style = list(
      cell_text(align = "center") # Center the text
    ),
    locations = cells_body(columns = everything())
  ) %>%
  tab_style(
    style = list(
      cell_borders(
        sides = "bottom", color = "black", weight = px(1)
      )
    ),
    locations = cells_column_labels(everything())
  ) %>%
  opt_table_lines("none") # Remove external table lines

apa.corr
```


```{r}
k.mod1 <- with(imp, glm(I(cat.atl=="High") ~ x1tchapp+x2kage_r+x2povty+kndr_par_ed+
                        x1tchapp+x2prnapp+x2inbcnt+x2attnfs+
                        a1yrstch+a1hghstd+
                        x2pltot+x2clsnss+x2pltot:x2clsnss, 
                      family="binomial"))
summary(pool(k.mod1))

naniar::miss_summary(dll.atl.kndr)
naniar::miss_summary(dll.atl.frst)
```

#Logistic Regression - Account for conflict, test Closeness - Clustered SE
```{r}
#use this model for unweighted results - 9/17

# d= data set used to create OG imp object

cat.mod <- lapply(imp, FUN=function(data){
  glm.cluster(data= d, 
              formula=I(cat.atl=="High") ~ x1tchapp+x2kage_r+x2povty+kndr_par_ed+
              x1tchapp+x2prnapp+x2inbcnt+x2attnfs+
              a1yrstch+a1hghstd+
              x2pltot+x2cnflct+x2clsnss+x2pltot:x2clsnss, 
            cluster=d$s2_id,
            family="binomial") 
})
# extract parameters and covariance matrix
betas.2 <- lapply( cat.mod, FUN=function(rr){ coef(rr) } )
vars.2 <- lapply( cat.mod, FUN=function(rr){ vcov(rr) } )
# conduct statistical inference
summary( miceadds::pool_mi( qhat=betas.2, u=vars.2))


```

# Logistic Regression - PCA Relationship - Clustered SE
```{r}
#still unclear why %missing column is populated - 9/17

rslt.3 <- with(mids.pca, glm(I(cat.atl=="High") ~ x1tchapp+x2kage_r+x2povty+kndr_par_ed+
                        x1tchapp+x2prnapp+x2inbcnt+x2attnfs+
                        a1yrstch+a1hghstd+
                        x2pltot+relation.pca+x2pltot:relation.pca, 
                        family=binomial(link = 'logit')))

models <- rslt.3$analyses

betas.3 <- lapply(models, function(model) coef(model))
vars.3 <- lapply(models, FUN = function(x){vcovCL(x, cluster = mids.pca[[1]]$s2_id)}) #vcovCL is in the sandwich package
  # conduct statistical inference
summary(miceadds::pool_mi(betas.3, vars.3))


#investigating missinfo column

missing_summary <- lapply(mids$imp, function(df) {
  sapply(df, function(col) sum(is.na(col)))
})

print(sapply(imp.list, function(df) any(is.na(df))))

```


```{r}
#DO NOT USE 
rslt.3 <- lapply(imp.list, FUN=function(data){ 
  glm.cluster(data= d, 
              formula=I(cat.atl) ~ x1tchapp+x2kage_r+x2povty+kndr_par_ed+
                        x1tchapp+x2prnapp+x2inbcnt+x2attnfs+
                        a1yrstch+a1hghstd+
                        x2pltot+relation.pca+x2pltot:relation.pca,
                        cluster=d$s2_id,
                        family="binomial")
  })
#this approach doesn't work bc it is calling on vars stored in d (df used for imputation) and PCA scores where added after imputation

betas.3 <- lapply(rslt.3, FUN=function(rr){ coef(rr) })
vars.3 <- lapply(rslt.3, FUN=function(rr){ vcov(rr) }}) #vcovCL is in the sandwich package
  # conduct statistical inference
summary(miceadds::pool_mi(qhat= betas.3, u=vars.3))
```


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
